---
title: "Starring and unstarring a Drive file with an encrypted credential"
format: html
resource_files:
- "service_account_cred_enc.json"
---

```{r }
#| label: setup
#| include: FALSE
can_decrypt <- gargle::secret_has_key("GOOGLEDRIVE_DEPLOY_DEMO_KEY")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = can_decrypt
)
```

```{r}
#| eval: !expr '!can_decrypt'
#| echo: FALSE
#| results: 'asis'
cat("*Decryption key is unavailable, so no code will be evaluated.*")
```

The following chunk reads the stored token from file, using the environment variable `"GOOGLEDRIVE_DEPLOY_DEMO_KEY"` to decrypt it, and tells googledrive to use it.

```{r}
library(googledrive)

try(drive_auth(
  path = gargle::secret_decrypt_json(
    "service_account_cred_enc.json",
    key = "GOOGLEDRIVE_DEPLOY_DEMO_KEY"
  )
))
```

We wrap that in `try()` to guard against the scenario where the token *can* be decrypted, but auth still fails.
For example, maybe the service account has been deleted or had certain permissions revoked.
If auth has been successful, the `drive_user()` call below reveals details about the account associated with the token.
If auth has not been successful, `drive_user()` will throw an error.
Other functions that can be helpful for confirming the validity of a re-loaded token are `gargle::token_tokeninfo()` and `gargle::token_userinfo()`.

```{r}
#| error: TRUE
drive_user()
```

## Do something on Drive

Our toy task is to star or unstar a file on Drive.

### Make sure the file exists

We're going to work with a file named "chicken_poem.txt".
Do we already have a Drive file named "chicken_poem.txt"?
If not, create it.

```{r}
poem <- drive_find("chicken_poem.txt")
if (nrow(poem) < 1) {
    poem <- drive_example_local("chicken.txt") |>
        drive_upload("chicken_poem.txt")
}
(poem_id <- poem$id)
```

### Star or unstar the file

Is "chicken_poem.txt" starred?
If yes, unstar it.
If no, star it.

```{r}
(x <- drive_reveal(poem_id, "starred"))
drive_update(poem_id, starred = !x$starred)
```

Recheck the starred status of "chicken_poem.txt".
It should be the opposite of where we started.

```{r}
drive_reveal(poem_id, "starred")
```

This small example can be used as the basis for deploying content to a platform such as Posit Connect that works with googledrive.
